A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Consistent use of "Fig" rather than "Figure"
Simplify the statement

%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
In contrast to the existing solutions targeting in static data sets\cite{DIaas, MARSA}, we aim for processing the high volume, high velocity and high variety of real-time data streams\cite{BigData}. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading. Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, trusted third-party authority like CA is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following four essential ones:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
\end{itemize}

@@

\subsection{The Message Streams}
A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload. To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem. Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.

>>>>

%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
In contrast to the existing solutions targeting in static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity and high variety of real-time data streams\cite{BigData}. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
Among the challenges of data trading platform\cite{BigDataMarket}, the following characteristics are required:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
\end{itemize}

@@

\subsection{The Message Streams}
A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload. To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem. Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Fig.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
